---
title: "gnemeAnnotation"
author: Sylvain Schmitt
date: April 28, 2022
output:
  github_document: 
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
rm(list = ls()) ; invisible(gc()) ; set.seed(42)
library(knitr)
library(tidyverse)
theme_set(bayesplot::theme_default())
opts_chunk$set(echo = F, message = F, warning = F, fig.height = 6, fig.width = 8,
               cache = F, cache.lazy = F)
```

[`singularity` & `snakemake`](https://github.com/sylvainschmitt/snakemake_singularity) workflow to annotate genomes.

```{r dag, fig.cap="Workflow."}
knitr::include_graphics("dag/dag.svg")
```

# Installation

- [x] Python ≥3.5
- [x] Snakemake ≥5.24.1
- [x] Golang ≥1.15.2
- [x] Singularity ≥3.7.3
- [x] This workflow

```{bash, eval=F, echo=T}
# Python
sudo apt-get install python3.5
# Snakemake
sudo apt install snakemake`
# Golang
export VERSION=1.15.8 OS=linux ARCH=amd64  # change this as you need
wget -O /tmp/go${VERSION}.${OS}-${ARCH}.tar.gz https://dl.google.com/go/go${VERSION}.${OS}-${ARCH}.tar.gz && \
sudo tar -C /usr/local -xzf /tmp/go${VERSION}.${OS}-${ARCH}.tar.gz
echo 'export GOPATH=${HOME}/go' >> ~/.bashrc && \
echo 'export PATH=/usr/local/go/bin:${PATH}:${GOPATH}/bin' >> ~/.bashrc && \
source ~/.bashrc
# Singularity
mkdir -p ${GOPATH}/src/github.com/sylabs && \
  cd ${GOPATH}/src/github.com/sylabs && \
  git clone https://github.com/sylabs/singularity.git && \
  cd singularity
git checkout v3.7.3
cd ${GOPATH}/src/github.com/sylabs/singularity && \
  ./mconfig && \
  cd ./builddir && \
  make && \
  sudo make install
# detect Mutations
git clone git@github.com:sylvainschmitt/genomeAnnotation.git
cd genomeAnnotation
```

# Usage

## Locally

```{bash, eval=F, echo=T}
snakemake -np -j 3 --resources mem_mb=10000 # dry run
snakemake --dag | dot -Tsvg > dag/dag.svg # dag
snakemake --use-singularity -j 3 --resources mem_mb=10000 # run
```


## HPC

```{bash, eval=F, echo=T}
module load bioinfo/snakemake-5.25.0 # for test on node
snakemake -np # dry run
sbatch job.sh # run
snakemake --dag | dot -Tsvg > dag/dag.svg # dag
```

# Workflow

## Transposable elements (TE)

### [repeat_masker](https://github.com/sylvainschmitt/genomeAnnotation/blob/main/rules/repeat_masker.smk)

* Tools: [RepeatMasker](https://stab.st-andrews.ac.uk/wiki/index.php/Repeatmasker)
* Singularity: docker://pegi3s/repeat_masker

### [repeat_modeler](https://github.com/sylvainschmitt/genomeAnnotation/blob/main/rules/repeat_modeler.smk)

* Tools: [RepeatModeler](https://github.com/Dfam-consortium/RepeatModeler)
* Singularity: docker://dfam/tetools
  
## Genes

### [braker_prot](https://github.com/sylvainschmitt/genomeAnnotation/blob/main/rules/braker_prot.smk)

* Tools: [braker.pl](https://github.com/Gaius-Augustus/BRAKER#running-braker)
* Singularity: docker://blaxterlab/braker

## Functional annotation
